### 2010-03-11 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: transform my TeX comments into readable (haha) notes.

@@

@@

@@

%%! I suspect we don't, space-wise

@@

@@

@@

%%! Actual implementation as a generic function??!

@@

%%! FreeMonad takes a damned tagged description

@@

%%! Should we stop here? Or show off some madness?

>>>>

\note{ Need care: motivating motivation of indexing. }

@@

\note{ I will need some tutorial on this ad-hoc notion of definitional
  equality. Or what Conor's meant with that. }

@@

\note{ Anything else? }

@@

\note{ I suspect we don't implement vectors, space-wise }

@@

\note{Is that convincing? Worth saying? Anything else?}

@@

\note{ I'm not familiar with this, I need to get into the paper. }

@@

\note{ Actual implementation of forcing as a generic function??! }

@@

\note{ FreeMonad takes a damned tagged description }

@@

\note{ Should we stop here? Or show off some madness? }
